Example script the `dispRity` paper

### 2018-04-20 paper/dispRity_paper.tex
Updated paper and figures in eps

\documentclass[12pt,letterpaper]{article}
\usepackage{natbib}

%Packages

\usepackage{xcolor}
\usepackage{color,soul}
\usepackage{pdflscape}
\usepackage{fixltx2e}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{float}
\usepackage{latexsym}
\usepackage{url}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{array}
\usepackage[version=3]{mhchem}
\usepackage{ifthen}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amstext}
\usepackage{enumerate}
\usepackage[osf]{mathpazo}
\usepackage{dcolumn}
\usepackage{lineno}
\usepackage{dcolumn}
\usepackage{hyphenat}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{float}
\restylefloat{table}
\newcolumntype{d}[1]{D{.}{.}{#1}}

@@

\begin{landscape}
\begin{table}
    \begin{tabular}{p{4cm}p{5cm}p{6cm}p{6cm}}
        \hline
        \textbf{in this manuscript} & \textbf{in} \texttt{\textbf{dispRity}} & \textbf{in palaeobiology} & \textbf{in ecology} \\ 
        \hline
        multidimensional space & matrix ($n\times k$) & morphospace, traitspace, etc. & ecospace, function-space, etc. \\
        \hline
        elements & rows ($n$) & taxa, specimen, etc. & taxa, field sites, environments, etc. \\
        \hline
        dimensions & columns ($k$) & ordination scores, distances, etc. & ordination scores, distances, etc. \\
        \hline
        subsets & matrix ($m \times k$, with $m \leq n$) & e.g. every element in a stratum or sharing the same ancestor & e.g. elements living in the same environment \\
        \hline
        disparity & a dimension-level 1 or 2 function$^1$ & disparity: e.g. the sum of variances \citep{Wills2001}, the average pairwise distances between taxa \citep{Foote01071994}, etc. & dissimilarity: e.g. ellipsoid volume \citep{DonohueDim}, convex hull volume \citep{cornwell2006trait}, etc. \\
        \hline
    \end{tabular}
    \caption{Glossary and equivalences between this manuscript, the \texttt{dispRity} package and terms commonly used in palaeobiology or ecology. $^1$See Fig. \ref{Fig:levels}.}
    \label{Tab:terms}
\end{table}
\end{landscape}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{workflowsvg.pdf} 
\caption{\disp package workflow: rectangles represent matrices; ellipses represent functions; plain black arrows indicate input/output; dashed grey arrows indicate output (though the summary, plot, and test function cannot be applied if no disparity has been calculated).}
\label{Fig:workflow}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.8\textwidth]{dispRity_fun.pdf}  %../inst/gitbook/dispRity_fun.pdf} 
\caption{Illustration of the different metric dimension-levels in the \disp package. In this example, each cell corresponds to a single value (e.g. a 8 $\times$ 7 matrix or a vector of eight elements).
A dimension-level 3 matrix would be a metric output a matrix (e.g. the function \texttt{stats::cor} to calculate the correlation between each dimension), a dimension-level 2 metric would output a vector (i.e. a distribution, e.g. \texttt{dispRity::variances} which calculates the variance within each dimension) and a dimension-level 1 metric would output a single value (e.g. \texttt{stats::sd} which calculates the standard deviation of the input matrix)}.
\label{Fig:levels}
\end{figure}

@@

\textbf{Table 2 (caption):} Where $k$ is the number of dimensions, $n$ the number of elements, $\Gamma$ is the Gamma distribution, $\lambda_i$ is the eigenvalue of each dimensions, $\sigma^{2}$ is their variance and $Centroid_{k}$ is their mean, $Ancestor_{n}$ is the coordinates of the ancestor of element $n$, $f(\mathbf{v}k)$ is function to select one value from the vector $\mathbf{v}$ of the dimension $k$ (e.g. it's maximum, minimum, mean, etc.), $R$ is the radius of the sphere or the product of the radii of each dimensions ($\displaystyle\prod_{i=1}^{k}R_{i}$ - for a hyper-ellipsoid). $^1$ by default that point is the centroid of the elements; $^2$ this function uses a fast estimation of the eigenvalue that only works in an ordinated space based on MDS or PCO (\textit{not} PCA).
\label{Tab:metrics}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{plot_example_group.pdf} 
\caption{\disp plot of disparity differences between groups.}
\label{Fig:plot_group}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{plot_example_time.pdf} 
\caption{\disp plot of disparity-through-time. The black line represents the median disparity (median sum of variances), the dark grey and light surfaces represent respectively the 50\% and 95\% confidence intervals.}
\label{Fig:plot_time}
\end{figure}

@@

\section{Package location}
The \disp package is available on the CRAN or at \url{https://github.com/TGuillerme/dispRity} with more associated information.

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{fullpage}
\usepackage{url}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{dcolumn}
\usepackage{lineno}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{float}
\restylefloat{table}
\newcolumntype{d}[1]{D{.}{.}{#1}}

@@

\begin{table}
    \begin{tabular}{p{4cm}p{5cm}p{6cm}p{6cm}}
        \hline
        \textbf{in this manuscript} & \textbf{in} \texttt{\textbf{dispRity}} & \textbf{in palaeobiology} & \textbf{in ecology} \\ 
        \hline
        multidimensional space & matrix ($n\times k$) & morphospace, traitspace, etc. & ecospace, function-space, etc. \\
        \hline
        elements & rows ($n$) & taxa, specimen, etc. & taxa, field sites, environments, etc. \\
        \hline
        dimensions & columns ($k$) & ordination scores, distances, etc. & ordination scores, distances, etc. \\
        \hline
        subsets & matrix ($m \times k$, with $m \leq n$) & e.g. every element in a stratum or sharing the same ancestor & e.g. elements living in the same environment \\
        \hline
        disparity & a dimension-level 1 or 2 function$^1$ & disparity: e.g. the sum of variances \citep{Wills2001}, the average pairwise distances between taxa \citep{Foote01071994}, etc. & dissimilarity: e.g. ellipsoid volume \citep{DonohueDim}, convex hull volume \citep{cornwell2006trait}, etc. \\
        \hline
    \end{tabular}
    \caption{Glossary and equivalences between this manuscript, the \texttt{dispRity} package and terms commonly used in palaeobiology or ecology. $^1$See Fig. \ref{Fig:levels}.}
    \label{Tab:terms}
\end{table}

@@

\begin{figure}[!htbp]
\centering
   %\includegraphics[width=1\textwidth]{workflowsvg.eps} 
\caption{\disp package workflow: rectangles represent matrices; ellipses represent functions; plain black arrows indicate input/output; dashed grey arrows indicate output (though the summary, plot, and test function cannot be applied if no disparity has been calculated).}
\label{Fig:workflow}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
   %\includegraphics[width=0.8\textwidth]{dispRity_fun.eps}  %../inst/gitbook/dispRity_fun.pdf} 
\caption{Illustration of the different metric dimension-levels in the \disp package. In this example, each cell corresponds to a single value (e.g. a 8 $\times$ 7 matrix or a vector of eight elements).
A dimension-level 3 matrix would be a metric output a matrix (e.g. the function \texttt{stats::cor} to calculate the correlation between each dimension), a dimension-level 2 metric would output a vector (i.e. a distribution, e.g. \texttt{dispRity::variances} which calculates the variance within each dimension) and a dimension-level 1 metric would output a single value (e.g. \texttt{stats::sd} which calculates the standard deviation of the input matrix)}.
\label{Fig:levels}
\end{figure}

@@

\textbf{Table 2 (caption):} Where $k$ is the number of dimensions, $n$ the number of elements, $\Gamma$ is the Gamma distribution, $\lambda_i$ is the eigenvalue of each dimensions, $\sigma^{2}$ is their variance and $Centroid_{k}$ is their mean, $Ancestor_{n}$ is the coordinates of the ancestor of element $n$, $f(\mathbf{v}k)$ is function to select one value from the vector $\mathbf{v}$ of the dimension $k$ (e.g. it's maximum, minimum, mean, etc.), $R$ is the radius of the sphere or the product of the radii of each dimensions ($\displaystyle\prod_{i=1}^{k}R_{i}$ - for a hyper-ellipsoid). $^1$ by default that point is the centroid of the elements; $^2$ this function uses a fast estimation of the eigenvalue that only works in an ordinated space based on MDS or PCO (\textit{not} PCA).

@@

\begin{figure}[!htbp]
\centering
   %\includegraphics[width=1\textwidth]{plot_example_group.eps} 
\caption{\disp plot of disparity differences between groups.}
\label{Fig:plot_group}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
   %\includegraphics[width=1\textwidth]{plot_example_time.eps} 
\caption{\disp plot of disparity-through-time. The black line represents the median disparity (median sum of variances), the dark grey and light surfaces represent respectively the 50\% and 95\% confidence intervals.}
\label{Fig:plot_time}
\end{figure}

@@

\section{Package location}
The \disp package is available on the CRAN at \url{https://cran.r-project.org/web/packages/dispRity/index.html} or on GitHub at \url{https://github.com/TGuillerme/dispRity} with more associated information.
All the versions of the package are archived on ZENODO with associated DOI \url{https://zenodo.org/record/1186467#.WtfbGsi-kW8}.
